---
title: "MyFitnessPal Case Github"
author: "Shoryoung Gong"
date: "2025-08-26"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
---
title: "MyFitnessPal Case Study Visualizations"
author: "Shoryoung Gong"
date: "`r Sys.Date()`"
output: html_document
---

```{r}
library(ggplot2)
library(dplyr)
library(scales)

# Parameters
total_users <- 220e6
revenue <- 310e6
sub_rate <- 0.0258
paying_users <- total_users * sub_rate
free_users <- total_users - paying_users
arpu <- revenue / total_users
monthly_churn <- 0.3786   # from case study (≈ 37.9%)
monthly_retention <- 1 - monthly_churn
expected_lifetime <- 1 / monthly_churn  # ~2.64 months

# Data for churn and retention
months <- 0:6
users_remaining <- total_users * (1 - monthly_churn) ^ months
churn_df <- data.frame(months, users_remaining)
retention_df <- data.frame(months, retention_rate = (1 - monthly_churn) ^ months)
arpu_df <- data.frame(Metric = "ARPU", Value = arpu)

# Churn curve
p1 <- ggplot(churn_df, aes(x=months, y=users_remaining/1e6)) +
  geom_line(color="red", size=1.2) +
  geom_point(color="darkred", size=2) +
  labs(title="Churn Curve: Users Over Time",
       x="Months Since Start", y="Users Remaining (millions)") +
  theme_minimal()

# Retention curve
p2 <- ggplot(retention_df, aes(x=months, y=retention_rate)) +
  geom_line(color="blue", size=1.2) +
  geom_point(color="darkblue", size=2) +
  labs(title="Retention Curve",
       x="Months Since Start", y="Retention Rate") +
  scale_y_continuous(labels=percent) +
  theme_minimal()


# Print all plots
p1; p2;

